### 2024-05-21 README.Rmd
Simplify extent in README

friction_surface <- get_friction_surface(
    surface = "motor2020",
    extent = matrix(
      data = c("111", "0", "112", 1),
      nrow = 2,
      ncol = 2,
      dimnames = list(
        c("x", "y"),
        c("min", "max")
      )
    )
  )
friction_surface
```

@@

Here it is:
```{r}
library(sdmtools)
sin <- sdmtools::make_africa_mask(
  type = "vector",
  countries = "SGP"
)
plot(sin)
```
Get the extent of that `SpatVector` in the format we need it.
```{r}
sin_ext <- ext_from_terra(sin)
sin_ext
```

We're going to see how long it takes to walk home from Changi Airport. So we'll 
download the walking-only friction surface this time.
```{r }
library(traveltime)
library(terra)

friction_singapore <- get_friction_surface(
    surface = "walk2020",
    extent = sin_ext
  )|> 
  mask(sin)

>>>>

friction_surface <- get_friction_surface(
    surface = "motor2020",
    extent = c(111,112,0,1)
  )
friction_surface
```

@@

Here it is:
```{r}
library(sdmtools)
sin <- sdmtools::make_africa_mask(
  type = "vector",
  countries = "SGP"
)
plot(sin)
```

We're going to see how long it takes to walk home from Changi Airport. So we'll 
download the walking-only friction surface this time.

We can feed in our `sin` `SpatVector` directly as the `extent`, instead of specifying by hand as above. 
```{r }
library(traveltime)
library(terra)

friction_singapore <- get_friction_surface(
    surface = "walk2020",
    extent = sin
  )|> 
  mask(sin)
